---
title: "LST-NDVI correlation coefficient NYSERDA MW Blocks"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Gather Pixel Frequency from Excel
```{r}
library(readxl)
ee_chart_Pre_Construction <- read_excel("results/ee-chart_Pre-Construction.xlsx")
View(ee_chart_Pre_Construction)
# 2010-14 Pre-Construction LST-NDVI Correlation Coefficient pixel frequency of
# NYSERDA MW Block Solar Farms, 
# Data Source: MODIS Satellite & NYSERDA, 
# Processed in Google Earth Engine,
# Data pixel frequency in Excel (in 'results' subdirectory)
```

```{r}
library(readxl)
ee_chart_Post_Construction <- read_excel("results/ee-chart_Post-Construction.xlsx")
View(ee_chart_Post_Construction)
# 2018-22 Post-Construction LST-NDVI Correlation Coefficient pixel frequency of
# NYSERDA MW Block Solar Farms, 
# Data Source: MODIS Satellite & NYSERDA, 
# Processed in Google Earth Engine,
# Data pixel frequency in Excel (in 'results' subdirectory)
```

## Load ggplot for creating graphs

```{r}
library(ggplot2)
# load R package for creating graphs
```

## Plots

#### Pre-Construction Pixel Frequency

```{r}
ggplot(ee_chart_Pre_Construction, aes(x=LST_NDVI_correlation_coefficient,y=Percentage_of_pixels)) + 
  geom_bar(aes(fill = LST_NDVI_correlation_coefficient), stat = "identity") +
  scale_fill_gradient2(low = '#062686', mid = '#FFFFFF', high = '#931118', midpoint = 0)
# Histogram of Pre-Construction LST-NDVI Correlation Coefficient pixel frequency
```

#### Post-Construction Pixel Frequency

```{r}
ggplot(ee_chart_Post_Construction, aes(x=LST_NDVI_correlation_coefficient,y=Percentage_of_pixels)) + 
  geom_bar(aes(fill = LST_NDVI_correlation_coefficient), stat = "identity") +
  scale_fill_gradient2(low = '#062686', mid = '#FFFFFF', high = '#931118', midpoint = 0)
# Histogram of Post-Construction LST-NDVI Correlation Coefficient pixel frequency
```

